---
title: "ABAxCOV Rev 9-23-22"
author: "Cassin Gonzales"
date: "9/23/2022"
output: html_document
---

## Load Data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load packages}
library(here)  
library(sjPlot)
library(tidyverse) 
library(haven) 
library(lme4) 
library(lmerTest)
library(MuMIn)
library(sjPlot)
library(emmeans)
library(modelsummary)
library(glmmTMB)
library(interactions) 
library(rstatix)
library(r2mlm)
library(broom.mixed)  
theme_set(theme_bw())
```

```{r load data}
abacov <- read_sav(here("data_files","ABAxCOV 2022","Abacov4_long.sav"))
```

```{r view data}
rmarkdown::paged_table(abacov)
```

```{r make factors}
abacov$Site <- as.factor(abacov$Site)
abacov$Sex <- as.factor(abacov$Sex)
abacov$Race <- as.factor(abacov$Race)
abacov$RaceTri <- as.factor(abacov$RaceTri)
abacov$Age <- as.numeric(abacov$Age)
abacov$PrimPay3 <- as.factor(abacov$PrimPay3)
abacov$PrimPay25 <- as.factor(abacov$PrimPay25)
abacov$Tele <- as.factor(abacov$Tele)
```

## Explore Data

```{r explore}
abacov %>%
    select(Site, Age, Race, PrimPay3, Hours, Time) %>%
    psych::pairs.panels(ellipses = FALSE, cex = 0.2, cex.cor = 1)
```

```{r spaghetti}
p1 <- ggplot(abacov, aes(x = Time, y = Hours)) + 
  geom_point() + 
  geom_line(aes(group = ID)) +  # add lines to connect the data for each person
  # add a mean trajectory
  stat_summary(fun = "mean", col = "red", size = 1, geom = "line")
p1
```
Based on this, we decided to go with 3 phases. The X axis shows specific months - 0 is March 2019 and 24 is February 2021.  Phase 1 (pre-covid) is march 2019 (0) - February 2020 (11). Phase 2 (crisis) is March 2020 (12) - May 2020 (14). Phase 3 (mitigation) is June 2020 (15) - February 2021 (24).  We decided to make a third phase because, after June 2020, the pre-covid pattern of hours each month resumes (just at a lower level).  

```{r meansd}
abacov %>%
  get_summary_stats(Hours, type = "mean_sd")

abacov %>%
  group_by(PrimPay3) %>%
  get_summary_stats(Hours, type = "mean_sd")

abacov %>%
  group_by(RaceTri) %>%
  get_summary_stats(Hours, type = "mean_sd")
```


```{r msd phase}
abacov %>%
  group_by(Phase) %>%
  get_summary_stats(Hours, type = "mean_sd")
```

```{r msd primpay}
abacov %>%
  group_by(Phase, PrimPay3) %>%
  get_summary_stats(Hours, type = "mean_sd")
```

```{r m sd race}
abacov %>%
  group_by(Phase, RaceTri) %>%
  get_summary_stats(Hours, type = "mean_sd")
```

## Unconditional Model

```{r unconditional}
ran_int <- lmer(Hours ~ 1 + (1 | ID), data = abacov)

summary(ran_int)
```
fixed effect:
Y00 is 58.47.  The estimated grand mean of hours for all participants is 58.47

random effect:
Uij = 643.1 is the deviation between jth individual and the grand mean.
Eij = 1072.1 this is the deviation of the ith timepoint from the mean hours received by a child. 

### ICC calculation
```{r ICC}
643.1/(643.1 + 1072.1)
```
The proportation of the variance in hours of therapy utillization that is due to between participant differences is .375.  


### Design Effect

Design effect = 1 + (average cluster size - 1) x ICC

```{r mean cluster size}
mean(table(abacov$ID))
```

mean cluster size = 24

```{r DE}
1 + 23*.375
```

design effect = 9.625


## Hypothesis Testing
```{r mod 1 no cov}
m_phase <- glmmTMB(Hours ~ Phase1 + Phase2 + Phase3 + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_phase)
```

During phase 1, hours of therapy significantly decreased by an average of 1.44 hours per month 
During phase 2, hours of therapy significantly decreased by an average of 10.8 hours per month 
During phase 3, hours of therapy significantly increased by an average of 2.4 hours per month 

```{r mod 1 season}
m_season <- glmmTMB(Hours ~ Phase1 + Phase2 + Phase3 + Season + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_season)
```

Clients recieved an average of 5.5 less hours per month during "off months" compared to "on months"


```{r mod1 cov}
m_covar <- glmmTMB(Hours ~ Phase1 + Phase2 + Phase3 + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_covar)
```

FINAL MAIN EFFECT MODEL
```{r Mod1}
m_covar5 <- glmmTMB(Hours ~ Phase1 + Phase2 + Phase3 + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_covar5)
```

March 2019: 90.61 hours
Phase 1: decrease 1.54 per month
phase 2: decrease 10.65 per month
phase three: increase 2.34 per month

### Model 2
```{r mod2}
m_race <- glmmTMB(Hours ~ (Phase1 + Phase2 + Phase3) * RaceTri + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_race)
```


```{r mod2 alt}
m_race5 <- glmmTMB(Hours ~ (Phase1 + Phase2 + Phase3) * Race + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_race5)
```

### Model 3
```{r mod3}
m_primpay <- glmmTMB(Hours ~ (Phase1 + Phase2 + Phase3) * PrimPay3 + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_primpay)
```

### Model 4

```{r mod4}
m_full1 <- glmmTMB(Hours ~ (Phase1 + Phase2 + Phase3) * PrimPay3 * RaceTri + Season + Age + Site + (Phase1 + Phase2 + Phase3 | ID), data = abacov, REML = TRUE)
summary(m_full1)
```